\systemEnding: Bootstrapping Domain-Specific Languages for Neurally-Guided Bayesian Program Learning

### 2018-07-04 poster.tex
progress on poster

\usetheme{confposter} % Use the confposter theme supplied with this template

\setbeamercolor{block title}{fg=ngreen,bg=white} % Colors of the block titles
\setbeamercolor{block body}{fg=black,bg=white} % Colors of the body of blocks
\setbeamercolor{block alerted title}{fg=white,bg=dblue!70} % Colors of the highlighted block titles
\setbeamercolor{block alerted body}{fg=black,bg=dblue!10} % Colors of the body of highlighted blocks
% Many more colors are available for use in beamerthemeconfposter.sty

@@

\newlength{\sepwid}
\newlength{\onecolwid}
\newlength{\twocolwid}
\newlength{\threecolwid}
\setlength{\paperwidth}{36in} % A0 width: 46.8in
\setlength{\paperheight}{54in} % A0 height: 33.1in
\setlength{\sepwid}{0.024\paperwidth} % Separation width (white space) between columns
\setlength{\onecolwid}{0.22\paperwidth} % Width of one column
\setlength{\twocolwid}{0.464\paperwidth} % Width of two columns
\setlength{\threecolwid}{0.708\paperwidth} % Width of three columns
\setlength{\topmargin}{-0.5in} % Reduce the top margin size
%-----------------------------------------------------------

@@

\usepackage{booktabs} % Top and bottom rules for tables

%----------------------------------------------------------------------------------------
%	TITLE SECTION 
%----------------------------------------------------------------------------------------
\newcommand{\system}{\textsc{DreamCoder}~}
\newcommand{\systemEnding}{\textsc{DreamCoder}}

@@

\author{Kevin Ellis, Lucas Morales, Mathias Sabl\'e Meyer, Armando Solar-Lezama, Joshua B. Tenenbaum} % Author(s)

@@

\begin{alertblock}{Wake/Sleep DSL Induction}

Lorem ipsum dolor sit amet, consectetur, nunc tellus pulvinar tortor, commodo eleifend risus arcu sed odio:
\begin{itemize}
\item Mollis dignissim, magna augue tincidunt dolor, interdum vestibulum urna
\item Sed aliquet luctus lectus, eget aliquet leo ullamcorper consequat. Vivamus eros sem, iaculis ut euismod non, sollicitudin vel orci.
\item Nascetur ridiculus mus.  
\item Euismod non erat. Nam ultricies pellentesque nunc, ultrices volutpat nisl ultrices a.
\end{itemize}

@@

\begin{block}{Introduction}

Lorem ipsum dolor \textbf{sit amet}, consectetur adipiscing elit. Sed commodo molestie porta. Sed ultrices scelerisque sapien ac commodo. Donec ut volutpat elit. Sed laoreet accumsan mattis. Integer sapien tellus, auctor ac blandit eget, sollicitudin vitae lorem. Praesent dictum tempor pulvinar. Suspendisse potenti. Sed tincidunt varius ipsum, et porta nulla suscipit et. Etiam congue bibendum felis, ac dictum augue cursus a. \textbf{Donec} magna eros, iaculis sit amet placerat quis, laoreet id est. In ut orci purus, interdum ornare nibh. Pellentesque pulvinar, nibh ac malesuada accumsan, urna nunc convallis tortor, ac vehicula nulla tellus eget nulla. Nullam lectus tortor, \textit{consequat tempor hendrerit} quis, vestibulum in diam. Maecenas sed diam augue.

Lorem ipsum dolor \textbf{sit amet}, consectetur adipiscing elit. Sed commodo molestie porta. Sed ultrices scelerisque sapien ac commodo. Donec ut volutpat elit. Sed laoreet accumsan mattis. Integer sapien tellus, auctor ac blandit eget, sollicitudin vitae lorem. Praesent dictum tempor pulvinar. Suspendisse potenti. Sed tincidunt varius ipsum, et porta nulla suscipit et. Etiam congue bibendum felis, ac dictum augue cursus a.

This statement requires citation \cite{Smith:2012qr}.

@@

\begin{figure}
\includegraphics[width=0.8\linewidth]{placeholder.jpg}
\caption{Figure caption}
\end{figure}

@@

\begin{column}{\twocolwid} % Begin a column which is two columns wide (column 2)

\begin{columns}[t,totalwidth=\twocolwid] % Split up the two columns wide column

\begin{column}{\onecolwid}\vspace{-.6in} % The first column within column 2 (column 2.1)

@@

\begin{block}{Materials}

The following materials were required to complete the research:

\begin{itemize}
\item Curabitur pellentesque dignissim
\item Eu facilisis est tempus quis
\item Duis porta consequat lorem
\item Eu facilisis est tempus quis
\end{itemize}

The materials were prepared according to the steps outlined below:

\begin{enumerate}
\item Curabitur pellentesque dignissim
\item Eu facilisis est tempus quis
\item Duis porta consequat lorem
\item Curabitur pellentesque dignissim
\end{enumerate}

@@

\begin{column}{\onecolwid}\vspace{-.6in} % The second column within column 2 (column 2.2)

%----------------------------------------------------------------------------------------
%	METHODS
%----------------------------------------------------------------------------------------

\begin{block}{Methods}

Lorem ipsum dolor \textbf{sit amet}, consectetur adipiscing elit. Sed laoreet accumsan mattis. Integer sapien tellus, auctor ac blandit eget, sollicitudin vitae lorem. Praesent dictum tempor pulvinar. Suspendisse potenti. Sed tincidunt varius ipsum, et porta nulla suscipit et. Etiam congue bibendum felis, ac dictum augue cursus a. \textbf{Donec} magna eros, iaculis sit amet placerat quis, laoreet id est. In ut orci purus, interdum ornare nibh. Pellentesque pulvinar, nibh ac malesuada accumsan, urna nunc convallis tortor, ac vehicula nulla tellus eget nulla. Nullam lectus tortor, \textit{consequat tempor hendrerit} quis, vestibulum in diam. Maecenas sed diam augue.

@@

\end{column} % End of column 2.2

\begin{alertblock}{Important Result}

Lorem ipsum dolor \textbf{sit amet}, consectetur adipiscing elit. Sed commodo molestie porta. Sed ultrices scelerisque sapien ac commodo. Donec ut volutpat elit.

\begin{columns}[t,totalwidth=\twocolwid] % Split up the two columns wide column again

\begin{column}{\onecolwid} % The first column within column 2 (column 2.1)

\begin{block}{Mathematical Section}

\begin{column}{\onecolwid} % The second column within column 2 (column 2.2)

%----------------------------------------------------------------------------------------
%	RESULTS
%----------------------------------------------------------------------------------------

\begin{block}{Results}

\end{column} % End of column 2.2

@@

\begin{column}{\onecolwid} % The third column

%----------------------------------------------------------------------------------------
%	CONCLUSION
%----------------------------------------------------------------------------------------

\begin{block}{Conclusion}

%----------------------------------------------------------------------------------------
%	ADDITIONAL INFORMATION
%----------------------------------------------------------------------------------------

\begin{block}{Additional Information}

%----------------------------------------------------------------------------------------
%	REFERENCES
%----------------------------------------------------------------------------------------

\begin{block}{References}

\nocite{*} % Insert publications even if they are not cited in the poster
\small{\bibliographystyle{unsrt}
\bibliography{sample}\vspace{0.75in}}

%----------------------------------------------------------------------------------------
%	ACKNOWLEDGEMENTS
%----------------------------------------------------------------------------------------

\setbeamercolor{block title}{fg=red,bg=white} % Change the block title color

\begin{block}{Acknowledgements}

\small{\rmfamily{Nam mollis tristique neque eu luctus. Suspendisse rutrum congue nisi sed convallis. Aenean id neque dolor. Pellentesque habitant morbi tristique senectus et netus et malesuada fames ac turpis egestas.}} \\

%----------------------------------------------------------------------------------------
%	CONTACT INFORMATION
%----------------------------------------------------------------------------------------

\setbeamercolor{block alerted title}{fg=black,bg=norange} % Change the alert block title colors
\setbeamercolor{block alerted body}{fg=black,bg=white} % Change the alert block body colors

\begin{alertblock}{Contact Information}

\begin{itemize}
\item Web: \href{http://www.my.edu/smithlab}{http://www.my.edu/smithlab}
\item Email: \href{mailto:john@smith.com}{john@smith.com}
\item Phone: +1 (000) 111 1111
\end{itemize}

\begin{center}
\begin{tabular}{ccc}
\includegraphics[width=0.4\linewidth]{logo.png} & \hfill & \includegraphics[width=0.4\linewidth]{logo.png}
\end{tabular}
\end{center}

\end{column} % End of the third column

>>>>

\usetheme{confposter} % Use the confposter theme supplied with this template 
\usepackage{exscale}
\setbeamercolor{block title}{fg=ngreen,bg=white} % Colors of the block titles
\setbeamercolor{block body}{fg=black,bg=white} % Colors of the body of blocks
\setbeamercolor{block alerted title}{fg=white,bg=dblue!70} % Colors of the highlighted block titles
\setbeamercolor{block alerted body}{fg=black,bg=dblue!10} % Colors of the body of highlighted blocks
% Many more colors are available for use in beamerthemeconfposter.sty

@@

\newlength{\sepwid}
\newlength{\onecolwid}
\newlength{\twocolwid}
\newlength{\threecolwid}
\setlength{\paperwidth}{36in} % A0 width: 46.8in
\setlength{\paperheight}{54in} % A0 height: 33.1in
\setlength{\sepwid}{0.024\paperwidth} % Separation width (white space) between columns
\setlength{\onecolwid}{0.22\paperwidth} % Width of one column
\setlength{\twocolwid}{0.464\paperwidth} % Width of two columns
\setlength{\threecolwid}{0.708\paperwidth} % Width of three columns
\setlength{\topmargin}{-0.5in} % Reduce the top margin size
%-----------------------------------------------------------
\usepackage{dsfont}
\DeclareMathOperator*{\argmin}{arg\,min} % thin space, limits underneath in displays
\DeclareMathOperator*{\argmax}{arg\,max} % thin space, limits underneath in displays

\newcommand{\Expect}{\mathds{E}} %{{\rm I\kern-.3em E}}
\newcommand{\indicator}{\mathds{1}} %{{\rm I\kern-.3em E}}
\newcommand{\expect}{\mathds{E}} %{{\rm I\kern-.3em E}}
\newcommand{\probability}{\mathds{P}} %{{\rm I\kern-.3em P}}
\newcommand{\lowerBound}{\mathscr{L}}
\newcommand{\code}[1]{{\texttt{#1}}}
\newcommand{\scode}[1]{{\texttt{#1}}}
\newcommand{\codechar}[1]{{\texttt{"#1"}}}

\usepackage{xcolor}
\definecolor{pop1}{HTML}{1F78b4}
\definecolor{pop2}{HTML}{164C13}
\definecolor{pop3}{HTML}{d95F02}
\definecolor{orange}{HTML}{d95F02}
\definecolor{teal}{HTML}{1b9e77}
\newcommand{\pop}[1]{\textcolor{pop1}{#1}}
\newcommand{\popp}[1]{\textcolor{pop2}{#1}}
\newcommand{\tree}[1]{\textcolor{pop3}{#1}}
\newcommand{\orange}[1]{\textcolor{orange}{#1}}
\newcommand{\teal}[1]{\textcolor{teal}{#1}}

@@

\usepackage{booktabs} % Top and bottom rules for tables
\usepackage{tabularx}
%----------------------------------------------------------------------------------------
%	TITLE SECTION 
%----------------------------------------------------------------------------------------
\newcommand{\system}{\textsc{DreamCoder}~}
\newcommand{\systemEnding}{\textsc{DreamCoder}}

@@

\author{Kevin Ellis, Lucas Morales, Mathias Sabl\'e Meyer, Maxwell Nye, Armando Solar-Lezama, Joshua B. Tenenbaum} % Author(s)

@@

\begin{alertblock}{Wake/Sleep DSL Induction}
  \textbf{Domain Specific Language (DSL):}
  A finely-tuned program representation, specialized to a domain of programming tasks.
  Prior work in program learning  largely uses hand-engineered DSLs.

  \textbf{Contribution:} the \system algorithm,
  which bootstraps a learned DSL while jointly training
  a neural net to search for programs in the learned DSL

  \textbf{Approach:} given a few hundred programming tasks, alternatingly:
  \begin{itemize}
  \item \textbf{Wake}: synthesize programs
  \item \textbf{Sleep-R}: train neural net (\textbf{R}ecognition model)
    \item \textbf{Sleep-G}: improve DSL (\textbf{G}enerative model)
    \end{itemize}

  \textbf{Program representation:}
  Lisp-like; conditionals, variables, local functions

@@

\begin{block}{Bayesian framing}

  Observe $N$ \textbf{tasks}, written $\left\{x_n \right\}_{n = 1}^N$, each a program synthesis problem.

  Solve task $x_n$ with latent program $p_n$

  \textbf{Likelihood model} $\probability[x_n|p_n]$
  scores program $p_n$ on task $x_n$

  Latent  \textbf{DSL $\mathcal{D}$} acts as generative model over programs: $\probability[x|\mathcal{D}]$

$$
\underbrace{p_n^* =   \argmax_{p_n}\probability[x_n|p_n]\probability[p_n|\mathcal{D}^*]}_{\text{\textbf{Wake}}}
$$
\begin{equation*}
\underbrace{\mathcal{D}^* = \argmax_{\mathcal{D}}    \probability[\mathcal{D}]\prod_n\sum_{p_n}\probability[x_n|p_n]\probability[p_n|\mathcal{D}]}_{\textbf{\text{Sleep-G}}}
  \end{equation*}

\begin{block}{Neural recognition model}

  Neural network $Q(p|x)$
  predicts distribution over programs conditioned on tasks.
  Simple $Q$: just predicts probabilities of DSL productions.  Goal: learn to invert generative model
$$\underbrace{\min_Q \text{KL}\left(\probability[p|x,\mathcal{D}] || Q(p|x)\right) }_{\text{\textbf{Sleep-R}}}$$

Train on two sources of data:

  \begin{itemize}
  \item \textbf{Samples (``Dreams'') from DSL}: Unlimited data, but only high-quality if generative model $\mathcal{D}$ is good. Like Helmholtz Machine's recognition model training. Loss:
    \begin{equation*}
\expect_{(p,x)\sim\mathcal{D} }\left[\log Q(p|x)\right]
      \end{equation*}
  \item \textbf{Self-Supervised}: $(x_n,p_n)$ pairs discovered during waking. Loss:
    \begin{equation*}
 %\sum_{n = 1}^N\left[\sum_{(x_n,p_n)}
  \frac{\probability\left[x_n,p_n|\mathcal{D}\right]}{\sum_{(x_n,p_n')}\probability\left[x_n,p_n|\mathcal{D} \right]}\log Q(p_n|x_n)%\right]
      \end{equation*}
  \end{itemize}

@@

@@

\begin{column}{\threecolwid} % Begin a column which is two columns wide (column 2)

\begin{columns}[t,totalwidth=\threecolwid] % Split up the two columns wide column

\begin{column}{\threecolwid}\vspace{-.6in} % The first column within column 2 (column 2.1)

@@

\begin{block}{Model outputs for three different task domains}

\begin{table*} %[t!]
  \makebox[\textwidth][c]{
%    \scriptsize
  \tabcolsep=4pt
  %% \renewcommand\code\texttt
  %% \renewcommand\codechar[1]{\texttt{"#1"}}
  \newcommand{\helpSize}{0.25cm}
  \begin{tabular}{>{\hspace{-0em}}c<{\hspace{1em}}>{\hspace{1em}}c<{\hspace{1em}}>{\hspace{-1em}}c<{\hspace{1em}}>{\hspace{0em}}c<{\hspace{-1em}}}
    \toprule
    &{\normalsize List Functions}&{\normalsize Text Editing}&{\normalsize Symbolic Regression}\\\midrule
    \rotatebox[origin=c]{90}{\normalsize \pop{Programs} \& Tasks}&{\tabcolsep=7pt
      \begin{tabular}{cc}
        \begin{tabular}{c}
          \code{[7\, 2\, 3]}$\to $\code{[7\, 3]}         \\
          \code{[1\, 2\, 3\, 4]}$\to $\code{[3\, 4]} \\
          \code{[4\, 3\, 2\, 1]}$\to $\code{[4\, 3]} \\
          \pop{\code{$f(\ell) = $}\code{($f_1$ $\ell$ ($\lambda$ (x)}}\\
          \hspace{1.15cm}\pop{\code{(> x 2)))}}       \\
          \\
          \code{[2\, 7\, 8\, 1]}$\to $\code{8}               \\
          \hspace{0.15cm}\code{[3\, 19\, 14]}$\to $\code{19}                \\
          \pop{\code{$f(\ell) = $}\code{($f_2$ $\ell$)}}
        \end{tabular}
        &
        \hspace{-0.3cm}\begin{tabular}{c}
          \code{[7\, 3]}$\to $\code{False}                              \\
          \hspace{0.3cm}\code{[3]}$\to $\code{False}                    \\
          \hspace{-0.3cm}\code{[9\, 0\, 0]}$\to $\code{True\phantom{e}} \\
          \hspace{0.3cm}\code{[0]}$\to $\code{True\phantom{e}}                        \\
          \hspace{-0.3cm}\code{[0\, 7\, 3]}$\to $\code{True\phantom{e}}                \\
          \pop{\code{$f(\ell) = $}\code{($f_3$ $\ell$ 0)}}
        \end{tabular}
      \end{tabular}
    }
    &
    \hspace{-0.5cm}\begin{tabular}{c}
      +106 769-438$\to $106.769.438\\%&Nancy FreeHafer $\longrightarrow$ Dr. Nancy\\
      +83 973-831$\to $83.973.831\\
      \pop{$f(\text{\code{s}}) = $\code{(}$f_0$\code{  \codechar{.} \codechar{-}
      }}\\
      \hspace{1.25cm}\pop{\code{($f_0$ \codechar{.} \codechar{ }}}\\
      \hspace{1.4cm}\pop{\code{(cdr s)))}}\\
      ~\\
      Temple Anna H $\to $TAH\\
      Lara Gregori$\to $LG\\
      \pop{$f(\text{\code{s}}) = $\code{(}$f_2$\code{ s)}}\\
    \end{tabular}
    &
    \begin{tabular}{ccc}
      \includegraphics[width = 3em]{figures/functions/4.png}&&
      \includegraphics[width = 3em]{figures/functions/146}\\
      \pop{\code{$f($x$) = $($f_1$ x)}}& &   \pop{\code{$f($x$) = $($f_6$ x)}}\\
      ~\\
      \includegraphics[width = 3em]{figures/functions/112.png}&&
        \includegraphics[width = 3em]{figures/functions/92.png}
      \\
      \pop{\code{$f($x$) = $($f_4$ x)}}& &   \pop{\code{$f($x$) = $($f_3$ x)}}\\

    \end{tabular}
    ~\\
    \midrule
    \rotatebox[origin=c]{90}{\normalsize \popp{DSL}}&
    \hspace{0cm}\begin{tabular}{l}
      % $f_0($\code{r}$,\ell) \,=\, $\code{(foldr $\ell$ r ($\lambda$ (x a)}\\
      % \phantom{$f_0($\code{r}$,\ell) \,=\, $\code{(foldr}}\code{(cons (index (length a) $\ell$) a)))}\\
      % \hspace{\helpSize}($f_1$: \emph{Get the largest number})\\
      % $f_0(\ell) \,=\, $\code{(foldr $\ell$ 0 ($\lambda$ (x a)}\\\hspace{0.8cm}\code{ (if (> a x) a x)))}\\
      % \hspace{\helpSize}($f_1$: \emph{Get the largest number in $\ell$})\\
      %NOTE: this is the actual invention, but I removed a redundant lambda
      % below: $f_0(\ell,$\code{r}$) \,=\, $\code{(foldr r $\ell$ ($\lambda$ (x a) (cons x a)))}\\
      %% \popp{$f_0(\ell,$\code{r}$) \,=\, $\code{(foldr r $\ell$ cons)}}\\
      %% \hspace{\helpSize}($f_0$: \emph{Append lists }\code{r}\emph{ and  $\ell$})\\
      \popp{$f_1(\ell,$\code{p}$) \,=\, $\code{(foldr $\ell$ nil ($\lambda$ (x a)}}\\
      \hspace{4cm}\popp{\code{(if (p x) (cons x a) a)))}}\\
      \hspace{\helpSize}($f_1$: \emph{Higher-order filter function})\\\\
      %(lambda (fold $0 0 (lambda (lambda (if (gt? $0 $1) $0 $1)))))
      \popp{$f_2(\ell) \,=\, $\code{(foldr $\ell$ 0 ($\lambda$ (x a)}}\\
      \popp{\phantom{$f_2(\ell) \,=\, $}\code{(if (> a x) a x)))}}\\
      \hspace{\helpSize}($f_2$: \emph{Maximum element in list $\ell$})\\\\
      \popp{$f_3(\ell,$\code{k}$) \,=\, $\code{(foldr $\ell$ (is-nil $\ell$)}}\\
      \phantom{$f_1(\ell,$}
      \popp{\code{($\lambda$ (x a) (if a a (= k x))))}}\\
      \hspace{\helpSize}($f_3$: \emph{Whether $\ell$ contains }\code{k})
    \end{tabular}&

  \hspace{0.5cm}\begin{tabular}{l}
    \popp{$f_0($\code{s}$,$\code{a}$,$\code{b}$) \,=\, $\code{(map ($\lambda$
    (x)}}\\
    \popp{\hspace{1cm}\code{ (if (= x a) b x)) s)}}\\
      \hspace{\helpSize}($f_0$: \emph{substitutes characters)}\\\\
      \popp{$f_1($\code{s}$,$\code{c}$) \,=\, $\code{(foldr s s ($\lambda$ (x
      a)}\\\hspace{1.1cm}\popp{\code{ (cdr (if (= c x) s a))))}}}\\
      \hspace{\helpSize}($f_1$: \emph{Drop characters from }\code{s}\\
      \hspace{\helpSize}\phantom{($f_1$: }\emph{ until  }\code{c}\emph{ reached})\\\\
      \popp{$f_2($\code{s}$) \,=\, $\code{(unfold s is-nil car
      }}\\
      \popp{\hspace{1cm}\code{($\lambda$ (z) (}$f_1$\code{ z \codechar{ })))}}\\
        \hspace{\helpSize}($f_2$: \emph{Abbreviates  words})
      %%   \popp{$f_3($\code{a}$,$\code{b}$) \,=\, $\code{(foldr a b cons)}}\\
      %% \hspace{\helpSize}($f_3$: \emph{Concatenate strings }\code{a}\emph{ and }\code{b})
  \end{tabular}&

  \begin{tabular}{l}
    \popp{$f_0($\code{x}$)\,=\,$\code{(+ x real)}}\\
    \popp{$f_1($\code{x}$)\,=\,$\code{($f_0$ (* real x))} }\\
    \popp{$f_2($\code{x}$)\,=\,$\code{($f_1$ (* x (}$f_0$\code{ x)))}}\\
    \popp{$f_3($\code{x}$)\,=\,$\code{($f_0$ (* x (}$f_2$\code{ x)))}}\\
    \popp{$f_4($\code{x}$)\,=\,$\code{($f_0$ (* x (}$f_3$\code{ x)))}}\\
    \hspace{\helpSize}\emph{($f_4$: 4th order polynomial)}\\\\
    \popp{$f_5($\code{x}$)\,=\,$\code{(/ real x)}}\\
    \popp{$f_6($\code{x}$)\,=\,$\code{($f_5$ ($f_0$ x))}}\\
    \hspace{\helpSize}\emph{($f_6$: rational function)}\\

  \end{tabular}
  \\\bottomrule\\
\end{tabular}}\vspace{-0.5cm}
%}\label{initialExampleDSL}%\vspace{-0.5cm}
\end{table*}
Top: Tasks from three domains we apply our algorithm to, each followed by the programs \system discovers for them. Bottom: Several examples from learned DSL. Notice that learned DSL primitives can call each other, and that \system rediscovers higher-order functions like \code{filter} ($f_1$ under List Functions)
\end{block}

\begin{columns}[t,totalwidth=\threecolwid] % Split up the two columns wide column again

\begin{column}{\twocolwid} % The first column within column 2 (column 2.1)

\begin{block}{Fragment Grammars: Inducing a DSL}
Fragment grammars: first introduced in computational linguistics~\cite{tim}
\begin{figure}[b!]\tabcolsep=2pt
\centering  \begin{minipage}[c]{7.5cm}
  \begin{tikzpicture}[scale=2]
    \node [rotate=90] at (-2.5,-0.5) {prog.};

          \node(l1) at (0,0) {};
  \node[color=pop3](p1) at (-1,-1) {\code{+}};
  \node[color=pop3](n1) at (0.7,-0.9) {\code{1}};
  \node(x1) at (0,-1) {\code{1}};
  \draw[color=pop3] (l1.south) -- (p1.north);
  \draw[color=pop3] (l1.south) -- (n1.north);
  \draw[color=pop3] (-0.5,-0.45) -- (x1.north);

  \node(t) at (-0.5,0.5) {};
  \draw (l1.south) -- (t.south);
  \node(c) at (-1.5,-0.2) {\code{cons}};
  \draw (t.south) -- (c.north);

%    \draw  (l1.south) -- (-0.5,0.5);

  %% \node(c) at (-0.5,-1.5) {\code{-}};
  %% \node(z) at (0.5,-1.5) {\code{x}};

  %% \draw (0,-1) -- (c.north);
  %% \draw (0,-1) -- (z.north);

  \begin{scope}[shift={(0,-2.5)}]
      \node(l1) at (0,0) {};
  \node[color=pop3](p1) at (-1,-1) {\code{+}};
  \node[color=pop3](n1) at (0.7,-0.9) {\code{1}};
  %\node(x1) at (0,-1) {};
  \draw[color=pop3] (l1.south) -- (p1.north);
  \draw[color=pop3] (l1.south) -- (n1.north);
  \draw[color=pop3] (-0.5,-0.45) -- (0,-1);

  \node(c) at (-0.5,-1.5) {\code{car}};
  \node(z) at (0.5,-1.5) {\code{z}};

  \draw (0,-1) -- (c.north);
  \draw (0,-1) -- (z.north);

  \node [rotate=90] at (-2.3,-0.7) {prog.};

  \end{scope}

\begin{scope}[shift={(0,-5)}]
  \node[pop3](p1) at (-1,-1) {\code{+}};
  \node[pop3](n1) at (0.8,-0.7) {\code{1}};
  \node[pop3](a) at (0,-1) {\code{ }};
  %\node(x1) at (0,-1) {};
  \draw[pop3] (0,0) -- (p1.north);
  \draw[pop3] (0,0) -- (n1.north);
  \draw[pop3] (-0.55,-0.4) -- (a.north);
  \node [rotate=90] at (-2.3,-0.7) {frag.};

  \end{scope}

\end{tikzpicture}
  \end{minipage}
\hspace{0.1cm}\begin{tabular}{ll}
    \toprule
    Example synthesized programs &Proposed $\lambda$-expression\\\midrule
    %% \begin{tabular}{l}
    %%   \code{($\lambda$ ($\ell$) (map ($\lambda$ (x) (index x $\ell$))}\\
    %%   \phantom{\code{($\lambda$ ($\ell$) (map }}\code{(range (- (length $\ell$) 1))))}\\
    %%   \code{($\lambda$ ($\ell$) (map ($\lambda$ (x) (index x $\ell$))}\\
    %%   \phantom{\code{($\lambda$ ($\ell$) (map }}\code{(range (+ 1 1))))}\\
    %% \end{tabular}&
    %% \begin{tabular}{l}
    %%   \code{(map ($\lambda$ (x) (index x $\ell$))}\\
    %%   \phantom{\code{(map)}}\code{(range $\alpha$))}\\
    %% \end{tabular}\\\midrule
    \begin{tabular}{l}
      \code{($\lambda$ (s) (map ($\lambda$ (x)}\\
      \hspace{0.4cm}\code{ (if (= x '.') '-' x))) s)}\\
      \code{($\lambda$ (s) (map ($\lambda$ (x) }\\
      \hspace{0.4cm}\code{ (if (= x '-') ',' x))) s)}\\
      \end{tabular}&
    \begin{tabular}{l}      \code{($\lambda$ (s) (map ($\lambda$ (x)}\\\hspace{0.2cm}\code{   (if (= x $\alpha$) $\beta$ x))) s)}
      \end{tabular}
\\\bottomrule\\
\end{tabular}
\caption{\textbf{Left:} syntax trees of two programs sharing common structure,
highlighted in {\orange{orange}},
  from which we extract a fragment and add it to the DSL (bottom). \textbf{Right:} actual programs,
  from which we extract fragments that perform character substitutions.}\label{fragmentExample}
\end{figure}

@@

\begin{column}{\onecolwid} % The second column within column 2 (column 2.2)
\begin{block}{Ongoing work: Generative models for text}
\begin{figure}
\centering
\tiny
\tabcolsep=2pt
\vspace{0pt}
\begin{tabular}{cc}
\begin{tabular}{ccc}
\multicolumn{3}{c}{Tasks:}\\
\hline
cut&F &Moss Side \\ 
control&CL &Burnage \\
control&F & City Centre\\
cut& PCFL& Brooklands \\
\multicolumn{3}{c}{Learned generative models:}\\
\hline
\scode{\textbackslash l*\textbackslash l} & \scode{((\textbackslash
u\textbackslash u)*)\textbar F}& \scode{( \textbar\textbackslash
u\textbackslash w*)*} \\
\multicolumn{3}{c}{Samples from synthesized generative models:}\\
\hline
ya&DQDF & Vr DR \\ 
glrwfdcnc&F &BeF lKQ \\
mgs&F& W\\
piljnl& KI& kqBfZ 0 \\
kj& F& ON\\
zci& GL& Bttc \\
sxpm& F& S \\
\hline
\\
\end{tabular} 
&
\begin{tabular}{c}
\begin{tabular}{l}
\multicolumn{1}{c}{Learned DSL:}\\
\hline
$f_1() = $ \scode{\textbackslash u\textbackslash w*}\\
$f_2(x) = $ \scode{($x$|$f_1$)*} $=$ \scode{($x$|\textbackslash
u\textbackslash w*)*}\\
$f_3(x) = f_2(\scode{space}) = $\scode{( \textbar\textbackslash
u\textbackslash w*)*}\\
\hline
$f_4(x) = $ \scode{($x$*$x$)}\\
\emph{ (equivalent to regex `plus')}\\
$f_5() = f_4(\scode{\textbackslash l}) = \scode{\textbackslash
l*\textbackslash l}$\\
\hline
\end{tabular}
\\
\\
\includegraphics[width=.4\linewidth]{figures/nampiregexjoshcurve3.eps} 
\end{tabular}
\end{tabular}
\vspace{-.3cm}
\caption{regex stuff}
\end{figure}

@@

\begin{block}{Learning from Scratch?}

  \end{block}
\end{column}

@@

%% \begin{column}{\onecolwid} % The third column

%% %----------------------------------------------------------------------------------------
%% %	CONCLUSION
%% %----------------------------------------------------------------------------------------

%% \begin{block}{Conclusion}

%% \end{block}

%% %----------------------------------------------------------------------------------------
%% %	ADDITIONAL INFORMATION
%% %----------------------------------------------------------------------------------------

%% \begin{block}{Additional Information}

%% \end{block}

%% %----------------------------------------------------------------------------------------
%% %	REFERENCES
%% %----------------------------------------------------------------------------------------

%% \begin{block}{References}

%% \nocite{*} % Insert publications even if they are not cited in the poster
%% \small{\bibliographystyle{unsrt}
%% \bibliography{sample}\vspace{0.75in}}

%% \end{block}

%% %----------------------------------------------------------------------------------------
%% %	ACKNOWLEDGEMENTS
%% %----------------------------------------------------------------------------------------

%% \setbeamercolor{block title}{fg=red,bg=white} % Change the block title color

%% \begin{block}{Acknowledgements}

%% \small{\rmfamily{Nam mollis tristique neque eu luctus. Suspendisse rutrum congue nisi sed convallis. Aenean id neque dolor. Pellentesque habitant morbi tristique senectus et netus et malesuada fames ac turpis egestas.}} \\

%% \end{block}

%% %----------------------------------------------------------------------------------------
%% %	CONTACT INFORMATION
%% %----------------------------------------------------------------------------------------

%% \setbeamercolor{block alerted title}{fg=black,bg=norange} % Change the alert block title colors
%% \setbeamercolor{block alerted body}{fg=black,bg=white} % Change the alert block body colors

%% \begin{alertblock}{Contact Information}

%% \begin{itemize}
%% \item Web: \href{http://www.my.edu/smithlab}{http://www.my.edu/smithlab}
%% \item Email: \href{mailto:john@smith.com}{john@smith.com}
%% \item Phone: +1 (000) 111 1111
%% \end{itemize}

%% \end{alertblock}

%% \begin{center}
%% \begin{tabular}{ccc}
%% \includegraphics[width=0.4\linewidth]{logo.png} & \hfill & \includegraphics[width=0.4\linewidth]{logo.png}
%% \end{tabular}
%% \end{center}

%% %----------------------------------------------------------------------------------------

%% \end{column}
% End of the third column
